Hydrodynamics and rheology of a vesicle doublet suspension

### 2019-07-18 vesicle_code/docs/adhesion/adhesion.tex
yny adhesion.tex

%To investigate how two vesicles interact with each other in a planar extensional flow,
At the beginning of the first set of simulations (left panels in Figure~\ref{fig:extensionalNonsymmetric})
we place a vesicle at $(x,y)=(0,0)$, 
and the other vesicle at $(x,y) = (3,\triangle y)$ where the initial vertical displacement $\triangle y$ varies from
$\triangle y=0$ for the top row, $\triangle y = 0.02$ for the second row, to
$\triangle y =0.1$ for the bottom two rows in Figure~\ref{fig:extensionalNonsymmetric}.
The adhesion strength ${\cal H} = 0.7$ for the top three rows, and ${\cal H} =0.6$ for the bottom row.
The color coding is the membrane tension with the color bar on the right of each row. We note that the negative membrane tension in an
extensional flow is consistent with the speculation for a wrinkled membrane in the elongational flow \cite{KantslerSegreSteinberg2007_PRL}.

>>>>

%To investigate how two vesicles interact with each other in a planar extensional flow,
At the beginning of the first set of simulations (left panels in Figure~\ref{fig:extensionalNonsymmetric})
we place a vesicle at $(x,y)=(0,0)$, 
and the other vesicle at $(x,y) = (3,\triangle y)$ where the initial vertical displacement $\triangle y$ varies from
$\triangle y=0$ for the top row, $\triangle y = 0.02$ for the second row, to
$\triangle y =0.1$ for the bottom two rows in Figure~\ref{fig:extensionalNonsymmetric}.
The adhesion strength ${\cal H} = 0.7$ for the top three rows, and ${\cal H} =0.6$ for the bottom row.
The color coding is the membrane tension with the color bar on the right of each row. We note that the negative tension in an
extensional flow is consistent with the tension for a vesicle with finite bending forces \cite{Narsimhan2014_JFM} and the
speculation for a wrinkled membrane in the elongational flow \cite{KantslerSegreSteinberg2007_PRL}.
